Hidden Talents Multiverse Analysis

### 2021-02-07 README.Rmd
add preregistration links to README

## IMPORTANT

The file sizes of many output files produced by scripts in this repository are very large. As a consequence, these output files are not tracked here (see .gitignore). To preserve the directory structure, files named `0-placeholder.txt` have been added to output directories. This ensures that, if you were to run code that produces output not tracked here, the correct directory exists so files can be reproduced and saved.

@@

- Primary analysis figures
- Secondary analysis figures
  - Set 1
  - Set 2

>>>>

## IMPORTANT!!

The file sizes of many output files produced by scripts in this repository are very large. As a consequence, these output files are not tracked here (see .gitignore). To preserve the directory structure, files named `0-placeholder.txt` have been added to output directories. This ensures that scripts can reproduce and save output to the correct directory (without having to manually add them).

## Preregistration

Details about the participants, methods, procedures, and analysis plans can be found on the Open Science Framework (OSF). Below are the relevant links for different aspects of the project:

-   [OSF project](https://osf.io/6r95z/)
-   [Original preregistration](https://osf.io/d2gz6/)
-   [Overview of measures](https://osf.io/5kawy/), which fully describes what was collected (including measures not used/analyzed in this project). Specific variable codebooks for the current project are contained in this repository (see Codeboooks below).
-   [Final preregistration](https://osf.io/4vsnz/) which also contains a preliminary write-up of the Methods for an eventual publication
-   [Secondary analysis plan - set 1](https://osf.io/7fu35/)
-   [Secondary analysis plan - set 2](https://osf.io/wcauf/)

@@

-   Primary analysis figures

-   Secondary analysis figures

    -   Set 1
    -   Set 2
